Benchmarking Python Deep Learning Frameworks\\ on Language Modeling

### 2016-12-13 paper/main.tex
Add metrics tables

All our frameworks run a \texttt{Python} wrapper, with a \texttt{C++} backend.
\ms{TODO: more spiel?}
%TensorFlow's computation graph is pure \texttt{Python}, which makes it slower than other frameworks.

@@

\subsection{Implementation \& Hyperparameters}
In our experiments, we optimized for a standard language modeling objective: \textit{cross-entropy}.

@@

Traditionally, neural models are trained until their performance on a \textit{development} set stops improving. Therefore, a full epoch of training (where all the training data is used) is usually followed by a predictive pass through development data.
\section{Benchmarks}
\subsection{Time}
The first benchmark to look at is how long training takes. Table \ref{tab:timing} summarizes various breakdowns.
\begin{table}
\begin{tabular}{c|ccc}
Time & Dynet & TensorFlow & Theano \\ \hline
Convergence & & 35h 25' & \\
Train epoch & & 6h57' &  \\
Test epoch & & 7'45'' & \\
Train batch & & 5'' &  \\
Test batch & & $<$1'' & \\
\end{tabular}
\caption{\label{tab:timing}Total runtime on various subtasks.}
\end{table}

>>>>

All our frameworks run a \texttt{Python} wrapper, with a \texttt{C++} backend. Both TensorFlow and DyNet make extensive use of the Eigen library for C++, which provides fast low-level linear algebra for matrix and tensor operations. Theano's backend uses the BLAS linear algebra libraries instead.
\ms{TODO: more spiel?}
%TensorFlow's computation graph is pure \texttt{Python}, which makes it slower than other frameworks.

@@

\subsection{Implementation \& Hyperparameters}
In our experiments, we optimized for a standard language modeling objective: \textit{cross-entropy}. The built-in cross-entropy loss functions in each framework were slightly different, which could potentially affect the number of iterations required for convergence.

@@

Traditionally, neural models are trained until their performance on a \textit{development} set stops improving. Therefore, a full epoch of training (where all the training data is used) is usually followed by a predictive pass through development data.
\section{Benchmarks}
\subsection{Time}
The first benchmark to look at is how long training takes. Table \ref{tab:timing} summarizes various breakdowns.
\begin{table}
\begin{tabular}{c|ccc}
Time & Dynet & TensorFlow & Theano \\ \hline
Convergence & & 35h 25' & \\
Train epoch & & 6h57' &  \\
Test epoch & & 7'45'' & \\
Train batch & & 5'' &  \\
Test batch & & $<$1'' & \\
\end{tabular}
\caption{\label{tab:timing}Total runtime on various subtasks.}
\end{table}
\subsection{Function-level metrics}
Using NVidia's built-in GPU profiler, \verb!nvprof!, we measured various ways in which the different frameworks utilized the GPU hardware, specifically focusing on the matrix multiply operation implemented in the function \verb!magma_lds128_sgemm_kernel()!. Table \ref{tab:metrics} summarizes.

\begin{table}
\begin{tabular}{c|ccc}
Metric 										& Dynet & TensorFlow & Theano \\ \hline
\verb!achieved_occupancy!			&			&					&				\\
\verb!sm_efficiency!					&			&					&				\\
\verb!warp_efficiency!					&			&					&				\\
\verb!warp_nonpred_efficiency!	&			&					&				\\
\verb!global_hit_rate!					&			&					&				\\
\verb!local_hit_rate!					&			&					&				\\
\verb!dram_read_throughput!		&			&					&				\\
\verb!dram_write_throughput!		&			&					&				\\
\end{tabular}
\caption{\label{tab:metrics}Total runtime on various subtasks.}
\end{table}
